Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-12 CORL/example.tex
Added comment containing https://www.tablesgenerator.com/#
example.tex: Replaced unprojection_consistency_loss with unprojection_consistency_loss_without_reprojection
Meeting with Michael: June 12

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Textures make Better Simulators

``I can't believe it's not real!" %Definitely gonna delete this lol
 %via Neural Textures
 }

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		This figure is an overview of how TRITON works, showing all submodules and losses.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses between nodes.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

	In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses.
	\begin{enumerate}
		\item{
			Neural Textures $\tau\toL$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
			\begin{equation}
				\pi=\tau\toL(s)
			\end{equation}
			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
		}
		\item{
			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
			\begin{equation}
				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
			\end{equation}
			$T$ is a variation of MUNIT, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
		}
		\item {
			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
			\begin{equation}
				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
			\end{equation}
		}
		\item{
			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
			\begin{equation}
				\lTR \Rightarrow \pi \approx \ph
			\end{equation}
			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
		}

@@

\subsection{Neural Texture and Projection}

@@

	TRITON's neural texture module lets it  of objects, and thus take advantage of 3d geometric priors. By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.

	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

	These neural textures are not stored in raster form during training. Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors. During inference, however, these textures are rasterized to save both time and video memory.

@@

	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures. The trained fourier-feature textures also exhibit less noise than its raster counterparts. We think this is because they don't suffer as muchIt cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
	}
	\label{fig:texture_realism_ablation}
\end{figure}

@@

	\subsection{Ground Truth Comaprison}
\begin{table}[H]
	\begin{tabular}{l|llllllll}
		& \multicolumn{8}{c}{Three Block Dataset}                                                                                                                                                                                              \\
		& \multicolumn{4}{c|}{Masked}                                                                                       & \multicolumn{4}{c}{Unmasked}                                                                                     \\
		& \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c|}{LPIPS}                              & \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c}{LPIPS}                              \\
		Algorithm                              & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c}{Unsync} \\ \hline
		\textbf{TRITON w/o $\tau, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
		\textbf{TRITON w/o $\lUC, \lTR$}       & 0.0442                    & 0.0386                      & 0.00586                   & 0.00589                     & 0.285                     & 0.255                       & 0.0364                    & 0.0310                     \\
		\textbf{TRITON}                        & 0.0286                    & 0.0267                      & 0.00479                   & 0.00478                     & 0.117                     & 0.1157                      & 0.0123                    & 0.0122                     \\
		\textbf{CycleGAN}                      &                           &                             &                           &                             &                           &                             &                           &                            \\
		\textbf{CUT}                           &                           &                             &                           &                             &                           &                             &                           &                           
	\end{tabular}
\end{table}

@@

>>>>

\usepackage{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Neural Textures Make Better Simulators

``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
 }

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

	In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses. [[One or two sentences summarizing the flow - nothing more than that]].

	%JUNE 12:
	%TODO: MIgrate all four of these teasers into their respective subsections to save space.

	\begin{enumerate}
		\item{
			Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:

			%What is it...then how do we use it...

			(as the 1st sentence) Define Neural Neural Texture as a function taking....

			(as the 2nd sentence)
			Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...

			project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$.

% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.

			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
			\begin{equation}
				\pi=\tau\toL(s)
			\end{equation}
			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
		}
		\item{
			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
			\begin{equation}
				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
			\end{equation}
			$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
		}
		\item {
			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
			\begin{equation}
				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
			\end{equation}
		}
		\item{
			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
			\begin{equation}
				\lTR \Rightarrow \pi \approx \ph
			\end{equation}
			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
		}

@@

\subsection{Neural Neural Texture and Projection}

@@

    %JUNE 12:
    %Defining what it is and how it's used.
    %
    %Justify why we're calling it neural neural texture. Unlike previous papers [citations], we learn a neural network instead of a grid of pixels. To be explicit we call it neural neural texture. %%%%%% Previous papers were more like latent textures but ours is different: it is a funciton.  Previous works were called "Neural Textures" but we're going to call ours "Neural Neural Textures" - a subtype of neural textures.

% 	TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors. 
	Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.

%THIS WILL BE REPLACED BY SUMMARY SECTION
% 	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

@@

	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures. The trained fourier-feature textures also exhibit less noise than its raster counterparts. We think this is because they do not suffer as much. It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss_without_reprojection.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=25x0pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
	}
	\label{fig:texture_realism_ablation}
\end{figure}

@@

	\subsection{Ground Truth Comaprison}

	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
\begin{table}[H]
	\begin{tabular}{l|llllllll}
		& \multicolumn{8}{c}{Three Block Dataset}                                                                                                                                                                                              \\
		& \multicolumn{4}{c|}{Masked}                                                                                       & \multicolumn{4}{c}{Unmasked}                                                                                     \\
		& \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c|}{LPIPS}                              & \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c}{LPIPS}                              \\
		Algorithm                              & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c}{Unsync} \\ \hline
		\textbf{TRITON w/o $\tau, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
		\textbf{TRITON w/o $\lUC, \lTR$}       & 0.0442                    & 0.0386                      & 0.00586                   & 0.00589                     & 0.285                     & 0.255                       & 0.0364                    & 0.0310                     \\
		\textbf{TRITON}                        & 0.0286                    & 0.0267                      & 0.00479                   & 0.00478                     & 0.117                     & 0.1157                      & 0.0123                    & 0.0122                     \\
		\textbf{CycleGAN}                      &                           &                             &                           &                             &                           &                             &                           &                            \\
		\textbf{CUT}                           &                           &                             &                           &                             &                           &                             &                           &                           
	\end{tabular}
\end{table}

@@

    \subsection{Unsorted}
     	These neural textures are not stored in raster form during training. Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors. During inference, however, these textures are rasterized to save both time and video memory.
